---
title: "Dataset Exploration"
Author: 'By Akhila Kvns'
Date: "08 February, 2017"
output: html_document
---
## Setting path

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(reshape2)
```

```{r}
setwd("C:/Users/Innova/Downloads/data")
getwd()
```

```{r}
files <- list.files(pattern = "*.csv")
```

** In the above process, we have set the path to the folder containing all the data files.

## Combining Files

```{r}

my_filter = function(x){
  tmp_data <- read.csv(x, header=T, stringsAsFactors = TRUE,na.strings = c("NA","#DIV/0!",""))[,-3]
  filter(tmp_data,Country.or.Area %in% c("Argentina", "Algeria","Australia", "Angola", "Brazil", "Canada", "China", "France", "Germany", "India", "Indonesia", "Italy",
                                         "Japan", "Mexico", "Russian Federation", "Saudi Arabia", "South Africa", "United Kingdom",
                                         "Zimbabwe"))
} 

myfiles_test_full = do.call(rbind, lapply(files, my_filter))
```

```{r}
head(myfiles_test_full)

```

** We filtered the dataset by choosing some countries and combined all the data related to that specific countries.

## Plotting
```{r}
library(ggplot2)

qplot(Commodity, Country.or.Area, data=myfiles_test_full, shape = Flow)

```

** The above plot, shows the flow of the commodities for every country by distinct values.

## Bar Plot

```{r}
barplot1 <- table(myfiles_test_full$Country.or.Area, myfiles_test_full$Flow)
barplot(barplot1, main="Country vs Flow",
        xlab="Flow", col=c("darkblue","red", "yellow", "green", "black", "pink", "blue", "grey","violet", "brown", "orange", "purple"),
        legend = rownames(barplot1))

```


** The above bar chart, gives us the amount of flow done by each country.

** Out of the export, import, reimport and re export, the ratio of import is larger.

** We have, Venezuela as the highest exporter as well as the importer.



## Filtering the data

```{r}



str(myfiles_test_full)
clean_data <- data.frame(country = as.factor(myfiles_test_full$Country.or.Area),trade=myfiles_test_full$Trade..USD., year = as.factor(myfiles_test_full$Year),flow=as.factor(myfiles_test_full$Flow), Commodity = as.factor(myfiles_test_full$Commodity), weight = as.factor(myfiles_test_full$Weight..kg.))

pie_trade_country <- data.frame(country = character(), trade = integer())
levels(clean_data$country)

for(filter_country in levels(clean_data$country)){
  filter_list = clean_data[clean_data$country == filter_country,]
  trade_amount = sum(filter_list$trade)
  pie_trade_country = rbind(pie_trade_country,data.frame(country=c(filter_country),trade=c(trade_amount)))
}
```


** In the above, we have filtered the data by taking the necessay columns and also we have added the trade by each country into a single value.

## Pie Chart

```{r}
pie(pie_trade_country$trade, pie_trade_country$country, main= "trade vs Country")
```


** From the above pie chart, We can conclude that Germany and China are the leading countries based upon the trade usd.


## Stacked Area Chart

```{r}
library(ggplot2)
ggplot(clean_data, aes(x=year, y=trade, group=country, fill=country))+geom_area(position = "stack")

```


** The above stacked area chart, shows the increase in the trade of the countries year by year.


** China, Canada, France and Germany has the major trade from the year 1994 when compared to other countries.

## Stacked Bar Chart

```{r}
library(ggplot2)
library(reshape2)

ggplot(clean_data, aes(x= country, y=trade, fill=flow))+ geom_bar(stat = "identity", position="dodge")+scale_fill_brewer(palette = "Set1")

```

** The above stacked bar chart, shows the flow of the countries depending upon trade.

** China is the leading trador of export, import and also re import.

** Zimbabwe stands last in the trade of both export and import.

** The countries Angola, Algeria, Argentina, Brazil, Germany, India ,Indonesia, Japan, Mexico, Russian Federation,South Africa and Zimbabwe do not have any Trades of Re-export and Re-import